Pillar 2- Quick Topic Models

### 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd
saving correct file

catalogue_dtm <- tb_topic_model$DTM[[1]]
catalogue_lda <- tb_topic_model %>% filter(n_topic == "35") %>% pull(Model) %>%.[[1]]

@@

app_model <- app_topic_model %>%
  filter(n_topic == 65)

#rm(course_all, course_following_semester)
```
## Saving files for APP
We save all requirements for the app.
```{r app files, eval = T}
save(app_topic_model, app_model, file = "App/Recommender System/data_topic_models.RDATA")
save(app_model, file = "./Output/app_model.RDATA")
```

>>>>

catalogue_dtm <- tb_topic_model$DTM[[1]]
catalogue_lda <- tb_topic_model %>% filter(n_topic == "65") %>% pull(Model) %>%.[[1]]

@@

app_model <- app_topic_model #%>%
  #filter(n_topic == 65)

#rm(course_all, course_following_semester)
```
## Saving files for APP
We save all requirements for the app.
```{r app files, eval = T}
save(app_model, file = "App/Recommender System/data_topic_models.RDATA")
save(app_model, file = "./Output/app_model.RDATA")
```
